---
title: "Data_Clinic"
author: "GCP"
institute: "浙江省人民医院GCP机构"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    code_folding: show
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true

---
```{r,include=FALSE}
library("reticulate")
use_condaenv('C:/ProgramData/anacod')
py_config()
repl_python()
```

# LUNG
## Data
```{python}
import pandas as pd
import numpy as np
from  scipy.stats import chi2_contingency
from scipy import stats
import numpy as np
#设置显示行数
pd.set_option('display.max_rows', 200)
#设置显示列数
pd.set_option('display.max_columns', 200)
data=pd.read_excel('E:/医学统计实习/肝癌/lung.xlsx')
data1=data.loc[data['失访类型'] != 2,:]
data1.iloc[:,:12].head()
```

data shape
```{python}
data1.shape
```

## Data Preprocessing
miss_rate
```{python}
a=data1.apply(lambda x: sum(x.isnull())/len(x))
a[a.values>0]
```

Missing value processing
```{python}
data1['BMI（kg/m^2）']=data1['BMI（kg/m^2）'].fillna(data1['BMI（kg/m^2）'].mean())
#分类型数据用众数填补缺失值，连续性数据用均值填补缺失值
data1['PS评分']=data1['PS评分'].fillna(data1['PS评分'].mode().values[0])
data1['抽烟']=[i for i in data1['抽烟'].fillna(data1['抽烟'].mode().values[0]).values]
data1['饮酒']=data1['饮酒'].fillna(data1['饮酒'].mode().values[0])
b=data1.apply(lambda x: sum(x.isnull())/len(x))
b[b.values>0]
```

## Table 1
```{python}
def T_Chisq_test():
    data=data1
    data_1=list(data.groupby(['病理诊断']))[0][1]#腺癌
    data_2=list(data.groupby(['病理诊断']))[1][1]#鳞癌
    col=data.columns[[1,4,5,7,9,11,15,17,70,71]]
    Ac=[]
    Scc=[]
    p=[]
    for i in range(len(col)):
        if i in [1,2,6,7,8,9]:
            mean1=np.round(np.mean(data_1.loc[:,col[i]]),2)
            std1=np.round(np.std(data_1.loc[:,col[i]]),2)
            mean2=np.round(np.mean(data_2.loc[:,col[i]]),2)
            std2=np.round(np.std(data_2.loc[:,col[i]]),2)
            Ac.append(str(mean1)+'('+str(std1)+')')
            Scc.append(str(mean2)+'('+str(std2)+')')
            p.append(np.round(stats.ttest_ind(data_1.loc[:,col[i]],data_2.loc[:,col[i]])[1],3))
        else:
            l=data_1.groupby(col[i])[col[i]].agg('count')
            m=data_2.groupby(col[i])[col[i]].agg('count')
            Ac.append(list(l))
            Scc.append(list(m))
            p.append(np.round(chi2_contingency(np.array([list(l),list(m)]))[1],3))
    table=pd.DataFrame({'Demographics':col,'Adenocarcinoma':Ac,'Squamous cell carcinoma':Scc,'p_value':p}) 
    return(table)
print(T_Chisq_test())
```

## Lasso
```{r}
library(glmnet)
#install.packages('glmnet')
data=read.csv('E:/study_HZ/k_lung.csv')
set.seed(1)
out=glmnet(data[,15:86],data[,10],alpha=1)
cv.out=cv.glmnet(data.matrix(data[,15:86]),data[,10],alpha=1)
lasso.mod=glmnet(data[,15:86],data[,10],alpha=1)
par(mfrow=c(2,1)) 
plot(cv.out,family='serif')
plot(lasso.mod,xlab='Penalty coefficient',family='serif')
```

## Multivariate Cox
K-M曲线
```{r}
data_xian=data[data$lung=='adenocarcinoma',]
data_lin=data[data$lung=='squamous cell carcinoma',]
best_coef=c(9,10,8,22,25,26,27,35,37,40,44,45,48,57,59,64,68,69,71,74,83,86)
#demo[2,best_coef]
library(survival)
library(survminer)
#install.packages('survminer')

coxdata1=data_xian[,best_coef]
coxdata2=data_lin[,best_coef]
fit1 <- survfit(Surv(生存期.月.,失访类型) ~ lung, data = data)

ggsurvplot(fit1,palette = c('#E7B800', '#2E9FDF'),
           data = data,
           risk.table =TRUE,
           pval =TRUE,
           legend.title = '',
           #conf.int =TRUE,
           xlab ='Time (months)', 
           ggtheme = theme_classic2())
```

腺癌
```{r}
res.cox1 <- coxph(Surv(生存期.月.,失访类型) ~., data =  coxdata1)
summary(res.cox1)
```

鳞癌
```{r}
res.cox2 <- coxph(Surv(生存期.月.,失访类型) ~., data =  coxdata2)
summary(res.cox2)
```

## Forest
腺癌
```{r}
ggforest(res.cox1,data=coxdata1,main="hazard ratio",cpositions=c(0.02,0.22,0.4),fontsize=0.8,refLabel="reference")
```

鳞癌
```{r}
ggforest(res.cox2,data=coxdata2,main="hazard ratio",cpositions=c(0.02,0.22,0.4),fontsize=0.8,refLabel="reference")

```

## Roc
```{r}
library(survivalROC)
Mayo= survivalROC(Stime=coxdata1$生存期.月.,
                    status=coxdata1$失访类型,
                    marker = coxdata1[,3],
                    predict.time =30,
                    method="KM")
plot(Mayo$FP, Mayo$TP, type="l",
       xlim=c(0,1), ylim=c(0,1),
       xlab=paste( "FP", "\n", "AUC = ",round(Mayo$AUC,3)),
       ylab="TP")

```

# MTHFR

## Original Data
```{r}
#result data
data1=read.csv('E:/医学统计实习/data1.csv')
colnames(data1)=c('id','age','sex','hcy','mthfr')
head(data1)
```
data1 shape
```{r}
dim(data1)
```

## Description Hcy
```{r}
hcy=data1$hcy
hist(hcy,breaks=200)
text(x=40,y=200,paste0('Hcy<15','   ',sum(ifelse(hcy<15,1,0)),
                       '      ','Hcy>15','   ',sum(ifelse(hcy>15,1,0))))
abline(v=15,lwd=1,col='red')
```

### Hcy and Age
```{r}
age=data1$age
hcy=data1$hcy
plot(age,hcy)
mod=lm(hcy~age)
abline(mod,col='red')
```

### Hcy and Sex (0-Woman  1-Man)
```{r}
#sex 0 Woman  1 Man
library(ggplot2)
sex=data1$sex
data1$sex=as.factor(data1$sex)
ggplot(data=data1)+
  geom_boxplot(aes(x=sex,y=hcy,group=sex))
```

## Description Sex
```{r}
data2<-data.frame(Sample<-c('Woman','Man'), 
                
                 value<-c(table(data1$sex)[1],table(data1$sex)[2]))

ggplot(data2,mapping = aes(Sample,value))+
  geom_bar(stat='identity',position='dodge') +
  geom_text(aes(label=value,y=value+10), position=position_dodge(0.9), vjust=0,family='serif')+
  labs(x = '',y = '') +
  theme(axis.title =element_text(size = 12),
        axis.text =element_text(size = 12, color = 'black'))+
  theme(axis.text.x = element_text(angle = 0, hjust = 0.3))+
  theme(text=element_text(family='serif'))
```

## Description Age
```{r}
age=data1$age
age=as.data.frame(age)
ggplot(data=age)+
  geom_boxplot(aes(y=age))
```

## MTHFR Result
### Plot
```{r}
mthfr=data1$mthfr
data2<-data.frame(Sample<-c('CC','CT','TT'), 
                 
                 value<-c(table(mthfr)[1],table(mthfr)[2],table(mthfr)[3]))

ggplot(data2,mapping = aes(Sample,value))+
  geom_bar(stat='identity',position='dodge') +
  geom_text(aes(label=value,y=value+10), position=position_dodge(0.9), vjust=0,family='serif')+
  labs(x = '',y = '') +
  theme(axis.title =element_text(size = 12),
        axis.text =element_text(size = 12, color = 'black'))+
  theme(axis.text.x = element_text(angle = 0, hjust = 0.3))+
  theme(text=element_text(family='serif'))
```

### MTHFR and Sex
```{r}
mthfr=data1$mthfr
sex=data1$sex
data4<-data.frame(Sample<-c('CC','CC','CT','CT','TT','TT'), 
                  sex=rep(c('Woman','Man'),3),
                  value<-c(table(mthfr,sex)[1,1]/sum(table(mthfr,sex)[1:3,1]),
                          table(mthfr,sex)[1,2]/sum(table(mthfr,sex)[1:3,2]),
                          table(mthfr,sex)[2,1]/sum(table(mthfr,sex)[1:3,1]),
                          table(mthfr,sex)[2,2]/sum(table(mthfr,sex)[1:3,2]),
                          table(mthfr,sex)[3,1]/sum(table(mthfr,sex)[1:3,1]),
                          table(mthfr,sex)[3,2]/sum(table(mthfr,sex)[1:3,2])))

ggplot(data4,mapping = aes(Sample,value,fill=sex))+
  geom_bar(stat='identity',position='dodge') +
  geom_text(aes(label=round(value,3),y=value+0.01), position=position_dodge(0.9), vjust=0,family='serif')+
  labs(x = '',y = 'frequence') +
  theme(axis.title =element_text(size = 12),
        axis.text =element_text(size = 12, color = 'black'))+
  theme(axis.text.x = element_text(angle = 0, hjust = 0.3))+
  theme(text=element_text(family='serif'))
```

### MTHFR (2-TT  1-CT  0-CC) and Hcy
```{r}
# mthfr 2 TT  1 CT  0 CC
mthfr=data1$mthfr
mthfr=as.character(mthfr)
da=data.frame(mthfr,hcy)
ggplot(data=da)+
  geom_boxplot(aes(x=mthfr,y=hcy,group=mthfr))+
  labs(x='')
```


## Linear Regression
```{r}
lr=lm(hcy~mthfr+age+sex,data1)
summary(lr)
```

## Logistic Regression
### mthfr classification
```{r}
hcy1=ifelse(data1$hcy>15,1,0)
##dummy variable
mthfr=data1$mthfr
tt=c()
ct=c()
count1=0
count2=0
count3=0
for (i in 1:length(mthfr)){
  if(mthfr[i]==2){
    tt[i]=1
    ct[i]=0
  }
  if(mthfr[i]==1){
    tt[i]=0
    ct[i]=1
  }
  if(mthfr[i]==0){
    tt[i]=0
    ct[i]=0
  }
}
pre=glm(hcy1~tt+ct+age+sex,family=binomial(link="logit"),data=data1)
summary(pre)
```

### continual
```{r}
pre=glm(hcy1~mthfr+age+sex,family=binomial(link="logit"),data=data1)
summary(pre)
```

